\PaperTitle

### 2024-05-04 paper/paper.tex
Results
Signed-off-by: Charles Hu <computerscience@verizon.net>

\begin{table}
  \caption{TCP stream count per website in the final cumulative data set}
  \label{tab:dataSize}
  \begin{tabular}{cc}
    \toprule
    Website & TCP Stream Count \\
    \midrule
    github & 100 \\
    google & 102 \\
    reuters & 102 \\
    wikipedia & 100 \\
    youtube & 102 \\
    \midrule
    Total & 506 \\
    \bottomrule
  \end{tabular}
\end{table}

@@

@@

@@

@@

@@

@@

\subsubsection{Model Results Overall}

>>>>

\begin{table}[h]
  \caption{TCP stream count per website in the final cumulative data set}
  \label{tab:dataSize}
  \begin{tabular}{cc}
    \toprule
    Website & TCP Stream Count \\
    \midrule
    github & 100 \\
    google & 102 \\
    reuters & 102 \\
    wikipedia & 100 \\
    youtube & 102 \\
    \midrule
    Total & 506 \\
    \bottomrule
  \end{tabular}
\end{table}

@@

The following section details the performance of the developed models on the final data set and their evaluation.

@@

The training and testing performance of the models were measured using accuracy.
Accuracy was used to provide a familiar and easily understandable metric for performance comparison.
Accuracy is specifically calculated as follows:

\begin{equation}
  \text{Accuracy} = \frac{\text{True Negative} + \text{True Positive}}{\text{Total Observations}}
\end{equation}

@@

The performance of the developed models was tested by having each model attempt to correctly classify the true website for a reserved testing set of TCP streams.
The following subsections describe the results of such testing.

@@

The performance of the logistic regression model is described in Table ~\ref{tab:log}.
Other models will be compared to this baseline to determine if they are effective at the web traffic classification task.

\begin{table}[h]
  \caption{Performance baseline for the models.}
  \label{tab:log}
  \begin{tabular}{ccc}
    \toprule
    Model & Training Accuracy & Testing Accuracy \\
    \midrule
    Log. reg. & 0.49010 & 0.55882 \\
    \bottomrule
  \end{tabular}
\end{table}

@@

The performance of the developed simple models on the web traffic classification task are described in Table ~\ref{tab:simple}.
DTC and KNN pass the baseline with over 75\% and 65\% accuracy respectively, indicating that these model designs are decently capable of predicting the correct website given some unidentified TCP stream.
3 models fail to pass the baseline: SVC, SGD, and Naive Bayes.

\begin{table}[h]
  \caption{Simple model performance.}
  \label{tab:simple}
  \begin{tabular}{ccc}
    \toprule
    Model & Training Accuracy & Testing Accuracy \\
    \midrule
    DTC & 1.0 & 0.75490 \\
    KNN & 1.0 & 0.65686 \\
    Log. reg. & 0.49010 & 0.55882 \\
    SVC & 0.52475 & 0.50980 \\
    SGD & 0.42822 & 0.5 \\
    Naive Bayes & 0.39851 & 0.40196 \\
    \bottomrule
  \end{tabular}
\end{table}

@@

The performance of the developed ensemble models on the web traffic classification task are described in Table ~\ref{tab:ensemble}.
Of the tested models, AdaBoost with a logistic regression function, AdaBoost with a SGD classifier, and bagging with a logistic regression function failed to pass the baseline minimum performance accuracy.
The rest of the developed models all passed the baseline minimum with bagging with a DTC, bagging with a KNN, and the RFC model performing the best across all ensemble models.
Bagging with a DTC in particular shows strong capacity to learn the data set complexity given its ability to correctly classify the testing set with over 83\% accuracy.

\begin{table}[h]
  \caption{Ensemble model performance.}
  \label{tab:ensemble}
  \begin{tabular}{ccc}
    \toprule
    Model & Training Accuracy & Testing Accuracy \\
    \midrule
    Bag - DTC & 0.93069 & 0.83333 \\
    Bag - KNN & 0.88366 & 0.78431 \\
    RFC & 0.97525 & 0.75490 \\
    Voting - Soft & 0.94554 & 0.75490 \\
    Ada - DTC & 0.98762 & 0.74510 \\
    Stacking & 0.95050 & 0.74510 \\
    Voting - Hard & 0.94307 & 0.72549 \\
    Ada - Log. reg. & 0.50248 & 0.50980 \\
    Ada - SGD & 0.54455 & 0.49020 \\
    Bag - Log. reg. & 0.48515 & 0.49020 \\
    \bottomrule
  \end{tabular}
\end{table}

\subsubsection{Overall Model Results}

Across both the simple models and ensemble models, bagging with a DTC performed the best with a testing accuracy of over 83\%.
All other developed models had accuracy scores below 80\%, with the closest model being bagging with a KNN with 78\% accuracy.
This suggests that bagging with a DTC is the most optimal model among those developed to use for confidently classifying web traffic based off of TCP streams.
